A 3D viewer for ImageJ

### 2008-04-16 viewer_paper/paper.tex
paper: One more word to orthoslices.

\subsection{Orthoslices}
The example of an orthoslice representation can be seen in figure \ref{fig:orthoslices}.
It consists of 3 orthogonal slices through the displayed volume. Together with the rotation capabilities, scrolling the slices through the volume offers a great way to follow neuritic fibres in brain tissue.

>>>>

\subsection{Orthoslices}
The example for an orthoslice representation can be seen in figure \ref{fig:orthoslices}. It is composed of 3 orthogonal slices through the volume, where each slice is parallel to two coordinate axes. This is opposed to oblique slices, which display arbitrary sections through a volume.

Together with the rotation capabilities, scrolling the slices through the volume offers a great way to follow neuritic fibres in brain tissue.
